\newglossaryentry{sustainability}
{
        name=sustainability,
        description={Is a complex attribute of various needs and activities of humanity. Broadly the subject of sustainability is fulfilled if it contributes to the goals defined by the UN \cite{UN_sustain}}
}

\newglossaryentry{main repo}
{
	name=main repository,
	description={Github repository containing all relevant data files, the thesis, code, csv files and images referenced in this work.\\
		 Link:https://github.com/Free2ndThought/MA}
}

\newglossaryentry{EN}{
        name=Europäische Norm,
        description={technical standards ratified by the CEM. CENELEC pr ETSI. To take effect, european standards have to be adopted into national standards}
}

\newglossaryentry{docker}{
		name= Docker,
	description={Virtualization tool, to encapsulate separate software images into single containers running on a 'clean' system. To facilitate communication the docker host system can access all images.}
}

\newglossaryentry{weekday}{
	name=weekday,
	description={Day of the week that is not considered a weekend day, in this case all days from monday to friday each week irrespective of holidays. Synonimous to wholeday, as all times between 0am and 11.59pm are considered.}
}

\newglossaryentry{workday}{
	name=workday,
	description={Section of a weekday/whole day between 8am and 6pm.}
}

\newglossaryentry{wholeday}{
	name=wholeday,
	description={Full day of the week that is not considered a weekend day. All measurements taken from 0am to 11.59pm are considered. Synonimous to weekday}
}


\newacronym{lcm}{LCM}{Least Common Multiple}

\newacronym{wwcr}{WWCR}{Workday to Weekday Consumption Ratio}

\newacronym{rpmt}{RPMT}{Recorded Performance Motivation Tool}

\newacronym{kpi}{KPI}{Key Performance Indicator}

\newacronym{emas}{EMAS}{Eco-Management and Audit Scheme}

\newacronym{ghg}{GHG}{Greenhouse Gas Protocol}

\newacronym{prtr}{PRTR}{Pollutant Release and Transfer Register}

\newacronym{sdg}{SDG}{Sustainable Development Goal}