\chapter{Methods}\label{chap:methods}
The following paragraphs of section~\ref{sec:measurement}, an overview over the installed measurement equipment is given, as well as a brief comment on usability on the data collected by the respective equipment.


\section{Measurement Equipment}\label{sec:measurement}
To establish a rudimentary realistic 'live environment laboratory', an assortment of different sensors was installed.
The sensors were distributed in an academic workplace, see section~\ref{sec:workplace} for further details.
The goal of this setup was to establish an accurate and realistic fingerprint of general electric energy consumption that takes place in a modern academic work environment.
Although further energy needs, like for example heating and cleaning appliances contribute to the overall energy consumption of a working space, the scope of this examination is limited to concrete energy consumption taking place on each individual workspace.
The paragraphs of section~\ref{subsec:powerMeasurement} give a detailed account on the hardware used to determine the concrete energy consumption values.
In section~\ref{subsec:attendance} the hardware to determine office attendance is discussed, and the examination of the data usability is provided.
\subsection{Power Consumption}\label{subsec:powerMeasurement}
To allow some differentiation between individual workplaces, different categories of office equipment and different workplace arrangements, 38 identical power measurement units were installed.
An overview of the technical specifications of the sensor model is given in table~\ref{fig:allnet-sensor}.
\begin{figure[t]}\label{fig:allnet-sensor}
    \begin{tabular*{\textwidth}{t}{l|c}}
        Attribute & Value \\
        Model name & All4212V3 \\

    \end{tabular*{\textwidth}}
\end{figure}

\subsection{Office Attendance}\label{subsec:attendance}

\subsection{Database and Networking}\label{subsec:databaseNetworking}


\section{Workplace Structure}\label{sec:workplace}


\section{Evaltuation Metrics \& Tools}\label{sec:metricsTools}

\subsection{\acrfullpl{kpi}}\label{subsec:KPI}

\subsection{\acrfull{rpmt}}\label{subsec:RPMT}
